A comparison of different methods for calculating tangent-stiffness matrices in a massively parallel computational peridynamics code.

### 2013-10-29 jacobian_calc_CMAME.tex
journal files say modeled object is 4x.5X.5 rather than what I stated

The methods were compared by running two sets of test problems where each method would solve a problem concurrently. Each test problem simulated a $\SI{4}{\meter}$ by $\SI{0.25}{\meter}$ by $\SI{0.25}{\meter}$ meter block of a material undergoing tension along the axis parallel to the long dimension of the block. The test problems were set up in \emph{Perdigm} as quasistatic equilibrium problems, where the displacement boundary conditions used to apply tension were applied gradually, in `load steps', and an equilibrium solution for each load step was achieved before applying the next load step. The purpose of applying the load in gradual steps is a widely used technique to ensure the Newton's method is always initialized near the actual solution and therefore likely to converge. The fictional material represented in the model had values of $\SI{1.515e4}{\mega\pascal}$ for bulk modulus, and $\SI{7.813e4}{\mega\pascal}$ for shear modulus. The peridynamic horizon, a length scale that effectively sets the bandwidth of tangent-stiffness in the computation, used in the test problems was always set to three times the nominal discretization size (i.e. node spacing in the particle discretization scheme). This results in a minimum tangent-stiffness matrix bandwidth of 7 (for an optimal node numbering scheme).

>>>>

The methods were compared by running two sets of test problems where each method would solve a problem concurrently. Each test problem simulated a $\SI{4}{\meter}$ by $\SI{0.5}{\meter}$ by $\SI{0.5}{\meter}$ meter block of a material undergoing tension along the axis parallel to the long dimension of the block. The test problems were set up in \emph{Perdigm} as quasistatic equilibrium problems, where the displacement boundary conditions used to apply tension were applied gradually, in `load steps', and an equilibrium solution for each load step was achieved before applying the next load step. The purpose of applying the load in gradual steps is a widely used technique to ensure the Newton's method is always initialized near the actual solution and therefore likely to converge. The fictional material represented in the model had values of $\SI{1.515e4}{\mega\pascal}$ for bulk modulus, and $\SI{7.813e4}{\mega\pascal}$ for shear modulus. The peridynamic horizon, a length scale that effectively sets the bandwidth of tangent-stiffness in the computation, used in the test problems was always set to three times the nominal discretization size (i.e. node spacing in the particle discretization scheme). This results in a minimum tangent-stiffness matrix bandwidth of 7 (for an optimal node numbering scheme).
